Parental Mentalization Across Cultures: Mind-mindedness and Parental Reflective Functioning in British and South Korean Mothers

### 2023-07-07 manuscript.Rmd
Fixed prior for Bayes factors

    #Performs bayse factor analyses on data.
    BFAMRC <- as.data.frame(correlationBF(nat[['AMRC']], nat[[val]]))
    BFNMRC <- as.data.frame(correlationBF(nat[['F_NMRC_Proportion']], nat[[val]]))

    #insert a new row into the dataframe for each condition.   
    df3[nrow(df3) + 1,] <- c(' ', val, round(corrAMRC$estimate[1], digits = 2), round(BFAMRC$bf, digits = 2), round(corrNMRC$estimate[1], digits = 2), round(BFNMRC$bf, digits = 2))

>>>>

    #Performs bayse factor analyses on data.
    BFAMRC <- as.data.frame(correlationBF(nat[['AMRC']], nat[[val]], rscale=2.055))
    BFNMRC <- as.data.frame(correlationBF(nat[['F_NMRC_Proportion']], nat[[val]], rscale=2.055))

    #insert a new row into the dataframe for each condition.   
    df3[nrow(df3) + 1,] <- c(' ', val, round(corrAMRC$estimate[1], digits = 3), round(1/BFAMRC$bf, digits = 2), round(corrNMRC$estimate[1], digits = 2), round(1/BFNMRC$bf, digits = 2))

### 2023-07-07 manuscript.tex
Fixed prior for Bayes factors

\caption{\label{tab:Table3prep}Associations between Maternal Mind-mindedness and the PRFQ Subscales}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{llcccc}
\toprule
\textbf{ } & \textbf{  } & \textbf{AMRC Pearson's r} & \textbf{AMRC Bayes Factor} & \textbf{NMRC Pearson's r} & \textbf{NMRC Bayes Factor}\\
\midrule
GB & CMS & 0 & 0.29 & -0.03 & 0.29\\
 & IC & 0.06 & 0.32 & 0.11 & 0.41\\
KO & CMS & 0.14 & 0.49 & 0.18 & 0.71\\
 & IC & 0.18 & 0.72 & 0.2 & 0.92\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:Table3prep}Associations between Maternal Mind-mindedness and the PRFQ Subscales}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{llcccc}
\toprule
\textbf{ } & \textbf{  } & \textbf{AMRC Pearson's r} & \textbf{AMRC Bayes Factor} & \textbf{NMRC Pearson's r} & \textbf{NMRC Bayes Factor}\\
\midrule
GB & CMS & 0.004 & 10.09 & -0.03 & 9.84\\
 & IC & 0.064 & 8.93 & 0.11 & 6.8\\
KO & CMS & 0.137 & 5.69 & 0.18 & 3.82\\
 & IC & 0.179 & 3.72 & 0.2 & 2.88\\
\bottomrule
\end{tabular}
\end{table}
